Timely Object Detection

### 2012-02-23 writeups/eccv12/eccv12.tex
sent draft to stefanie

\begin{table}
\centering
\caption{Summary of our notation.}
\label{tab:notation}
\begin{tabular}{|l|l|}
	\hline
	$\mathcal{I}$	&	image \\
	$C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
	$t$           & time into episode \\ 
	$T_s$, $T_d$  & start and deadline times \\ 
	$b_j$        	& belief state at step $j$ \\ 
	$\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
	$\mathcal{A}$ & set of actions $a_i \in \{\mathcal{L} \cup \mathcal{F}\}$\\ 
	$\mathcal{F}$ & set of featurization actions \\
	$\mathcal{L}$ & set of classification actions\\
	$o_i$					&	a real-valued observation upon executing $a_i \in \mathcal{L}$\\
	$\mathcal{O}$	& set of executed actions\\
	$\mathbf{o}$	& set of observations $\{o_k | a_k \in \mathcal{O}\}$\\
	$c(a)$				& cost of executing $a$, in units of $t$\\
	\hline
\end{tabular}\end{table}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.66\linewidth]
    {figures/evaluation.pdf}}
  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
  \label{fig:evaluation}
\end{figure}

@@

An action $a$ that consists of running a classifier $L_k$ returns a real-valued observation $o_k \sim P(O_k)$.
The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
We refer to the current set of observations as $\mathbf{o} = \{o_k | L_k \in \mathcal{O}\}$.

We define the state $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$\footnote{We write $P(C_k)$ to mean $P(C_k=1)$.}, the time into episode $t$, and the set of executed actions $\mathcal{O}$ and corresponding observations $\mathbf{o}$.

A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b_0$ and action $a_0$ to the next pair $b_1$, and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

@@

\section{Selecting actions} \label{sec:value}
Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
As our goal is to pick actions, we want to formulate a function $V(b,a)$ 	that assigns a value to a potential action, given the current state of the decision process.
We can then define the policy as simply
\begin{align}
\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} V(b,a)
\end{align}

Our system will be evaluated by some properties of the state $b$, and its performance is time-sensitive.
Accordingly, the value function should balance two terms: a function of the expected next belief state $b'$ after taking an action $a_i$, and the cost of $a_i$.
\begin{align}
V(b,a) = \mathbb{E}_{b' \sim P(b'|b,a)}[R(b')] - \lambda c(a|b)
\end{align}

We can be more explicit and split $b$ into its constitutents: (1) current set of observations $\mathbf{o}$; (2) posterior distribution $P(\mathbf{C}|\mathbf{o})$.
Accordingly, we have considerable flexibility in definining the ``reward'' function $R(b)$.

We consider a formulation of $R(b)$ based on information gain, as is common in problems of this type \todo{cite}.
The corresponding $R: P \mapsto \mathbb{R}$ is a function on the distribution over $\mathbf{C}$.
We note that as our goal is to reduce uncertainty of $P(\mathbf{C})$, it is natural to define $R$ as the negative entropy of the distribution given the observations.
\begin{align}
V(b,a)
&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[R(P(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O}) \\
&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[-H(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O})
\end{align}

@@

\subsection{The model of the belief state}
\begin{figure}[h!]
\centering
\subfloat[MRF]{\includegraphics[width=0.46\linewidth]{figures/inf_model_mrf.pdf}}
\subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
\caption{We present a point in the middle of the decision process, when some classifiers have already been observed.}
\label{fig:model}
\end{figure}

Evaluation of our policy depends on being able to compute certain marginals for the value function.
Toward this end, we employ an inference model to infer the marginals $P(C_i)$ given the observations $\mathcal{O}$.
It may also be useful to predict the marginals $P(L_i)$, as some formulations of our value function make use of this information.

We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
The parameters are trained on fully-observed data.
Exact inference is of course intractable in this model; we make use of Loopy Belief Propagation, which provides no general convergence guarantees but has been shown to work well empirically \todo{cite}.

\subsection{Submodularity} \label{sec:submodularity}
A natural question regarding our exposition so far is, why should we assume that a greedy policy would work well at all?
In fact, the problem as described exhibits interesting properties that here allow us to show that the greedy solution is near-optimal.

We first introduce the notion of submodularity.

\todo{write this out}

@@

\section{Implementation Details and Evaluation}
We use FastInf \cite{Jaimovich2010} for the learning and inference in our MRF model.

\section{Evaluation} \label{sec:evaluation}
- show that the greedy policy works better than random and better than fixed-order
- show that the reinfrocement learning policy works better than greedy, at least for the non-infogain rewards.

>>>>

\begin{table}
\centering
\caption{Summary of our notation.}
\label{tab:notation}
\begin{tabular}{|l|l|}
	\hline
	$\mathcal{I}$	&	image \\
	$C_k$         & presence of class $k \in \{1,\dots,K\}$ \\ 
	$t$           & time into episode \\ 
	$T_s$, $T_d$  & start and deadline times \\ 
	$b^j$        	& belief state at step $j$ \\ 
	$\pi$         & policy function, $b \mapsto a \in \mathcal{A}$ \\
	$\mathcal{A}$ & set of actions $a_i \in \{\mathcal{L} \cup \mathcal{F}\}$\\ 
	$\mathcal{F}$ & set of featurization actions \\
	$\mathcal{L}$ & set of classification actions\\
	$o_i$					&	a real-valued observation upon executing $a_i \in \mathcal{L}$\\
	$\mathcal{O}$	& set of executed actions\\
	$\mathbf{o}$	& set of observations $\{o_i | a_i \in \mathcal{O}\}$\\
	$c(a_i)$				& cost of executing $a_i$, in units of $t$\\
	\hline
\end{tabular}\end{table}

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.56\linewidth]
    {figures/evaluation.pdf}}
  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
  \label{fig:evaluation}
\end{figure}

@@

An action $a_i$ that consists of running a classifier $L_i$ returns a real-valued observation $o_i \sim P(O_i)$.
The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
We refer to the current set of observations as $\mathbf{o} = \{o_i | L_i \in \mathcal{O}\}$.

We define the state $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$\footnote{We write $P(C_k)$ to mean $P(C_k=1)$.}, the time into episode $t$, and the set of executed actions $\mathcal{O}$ with corresponding observations $\mathbf{o}$.

A classification \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b^0$ and action $a^0$ to the next pair $b^1$, and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

@@

\section{Selecting actions} \label{sec:value}
Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
As our goal is to pick actions, we want to formulate a function $V(b,a)$ 	that assigns a value to a potential action, given the current state of the decision process.
We can then define the policy as simply
\begin{align}
\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} V(b,a_i)
\end{align}

Our system will be evaluated by some properties of the state $b$, and its performance is time-sensitive.
Accordingly, the value function should balance two terms: a function of the expected next belief state $b'$ after taking an action $a_i$, and the cost of $a_i$.
\begin{align}
V(b,a_i) = \mathbb{E}_{b' \sim P(b'|b,a_i)}[R(b')] - \lambda c(a_i|b)
\end{align}

We can be more explicit and split $b$ into its constitutents, such as the current set of observations $\mathbf{o}$ and the posterior distribution $P(\mathbf{C}|\mathbf{o})$.
Accordingly, we have considerable flexibility in definining the ``reward'' function $R(b)$.

We consider a formulation of $R(b)$ based on information gain, as is common in problems of this type \todo{cite}.
The corresponding $R: P \mapsto \mathbb{R}$ is a function on the distribution over $\mathbf{C}$.
We note that as our goal is to reduce uncertainty of $P(\mathbf{C})$, it is natural to define $R$ as the negative entropy of the distribution given the observations.
\begin{align}
V(b,a_i)
&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[R(P(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O}) \\
&= \mathbb{E}_{o_i \sim P(O_i|\mathbf{C},\mathbf{o})}[-H(\mathbf{C}|\mathbf{o} \cup o_i)] - \lambda c(a_i|\mathcal{O})
\end{align}

@@

\subsection{The model of the belief state}
\begin{figure}[h!]
\centering
% \subfloat[MRF]{
\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf.pdf}
% }
% \subfloat[Local]{\includegraphics[width=0.46\linewidth]{figures/inf_model_loc.pdf}}
\caption{We present a point in the middle of the decision process, when some classifiers have already been observed.}
\label{fig:model}
\end{figure}

Evaluation of our policy depends on being able to efficiently compute the marginals $o_i$ and the expected information gain $I(\mathbf{C};O_i|\mathbf{o})$.
We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
The parameters are trained on fully-observed data.
Exact inference is of course intractable in a general model of this type, and quite slow for a model of our size.
Instead, we use Loopy Belief Propagation, which provides no general convergence guarantees but has been shown to work well empirically \todo{cite}.
The implementations details are given further in \autoref{sec:implementation}.

\subsection{Submodularity} \label{sec:submodularity}
A natural question regarding our exposition so far is, why should we assume that a greedy policy would work well at all?
In fact, the problem as described has properties that here allow us to show that the greedy solution is near-optimal.

We first introduce the notion of submodularity.
A set function $f$ is submodular if, whenever $A \subseteq B \subseteq E$ and $e \in E \setminus B$ it holds that
\begin{equation}
f(A \cup {e}) - f(A) \geq f(B \cup {e}) - f(B)
\end{equation}

Additionally, $f$ is called monotone if whenever $A \subseteq B$ it holds that $f(A) \leq f(B)$.
Nemhauser~\cite{Nemhauser1978} famously showed that a greedy algorithm applied to maximizing submodular monotone functions with $f(\emptyset)=0$ will obtain at least a $(1-1/e)$ fraction of the optimal solution.

Krause and Guestrin~\cite{Krause2005a} showed that the result applies to the problem of selecting a set of observations, such as in a sensor network, which maximally reduces uncertainty.
Specifically, they showed that if the function to be maximized by selecting observations $S$ is information gain of latent variables $U$ in a graphical model such that variables in $S$ are independent given $U$, the greedy selection algorithm gives the same near-optimal bound as  ~\cite{Nemhauser1978}, and that no polynomial-time algorithm can be guaranteed to give a better bound, unless $P \neq NP$.

\todo{adaptive submodularity \cite{Golovin2011}}

@@

\section{Implementation Details and Evaluation} \label{sec:implementation}
We use FastInf \cite{Jaimovich2010} for learning and inference in our MRF model.
The real-valued classifier responses $o_i$ are discretized into data-dependent bins for efficiency.

\section{Evaluation} \label{sec:evaluation}
- show that the greedy policy works better than random and better than fixed-order

- show that the reinforcement learning policy works better than greedy, at least for the non-infogain rewards.
